Parental Mentalization Across Cultures: Mind-mindedness and Parental Reflective Functioning in British and South Korean Mothers

### 2023-07-07 manuscript.Rmd
Minor fixes for final version

Two British mothers did not answer the age question, and another British mother’s HADS and PSI-SF responses could not be used due to a technical problem. The mother with missing HADS and PSI-SF data was excluded from the main analyses on cultural differences in parental mentalization reported below. 
Korean infants were older than British infants, *t*(`r round(iAge$parameter['df'], digits = 0)`) = `r round(iAge$statistic['t'], digits = 2)`, *p* = `r format.pval(iAge$p.value, digits = 1, eps = 0.001, nsmall = 3)`,
and British mothers were more highly educated than Korean mothers, *t*(`r round(mEdu$parameter['df'], digits = 0)`) = `r round(mEdu$statistic['t'], digits = 2)`, *p* = `r format.pval(mEdu$p.value, digits = 1, eps = 0.001, nsmall = 3)`, 
but the groups did not differ on maternal age, *t*(`r round(mAge$parameter['df'], digits = 0)`) = `r round(mAge$statistic['t'], digits = 2)`, *p* = `r format.pval(mAge$p.value, digits = 1, eps = 0.001, nsmall = 3)`. 
Infant age and maternal education were therefore included as additional covariates in the cultural differences analyses reported below. With regard to the separate categories of mind-related comments, only two mothers mentioned epistemic states and only eight mothers talked on the infant’s behalf. These categories are therefore not used in the analyses below. Table 1 shows the parenting style, mental health, and infant temperament data as a function of nationality. As shown Table 1, British mothers showed more positive parenting than did their Korean counterparts for both the self-report and observational measures. In terms of psychological well-being, Korean mothers scored more highly than British mothers for anxiety/depression and parenting distress. However, there were no significant differences between British and Korean mothers for reported or observed infant temperament and parent–child dysfunctional interaction (see Table 1).

@@

Table 2 shows the mind-mindedness data for the UK and Korean samples. Cultural differences in appropriate and non-attuned mind-related comments were investigated using ANCOVA, with nationality added as a fixed variable and infant age, maternal education, HADS scores, the PSI-SF subscale scores (parenting distress, parent–child dysfunctional interaction, difficult child), and Lab-TAB scores added as covariates. The correlations between the variables are shown in supplemental material 1. 
There was no main effect of nationality for appropriate mind-related comments, *F*(`r round(ancAMRC$rank-1, digits = 0)`, `r round(ancAMRC$df.residual, digits = 0)`) = `r round(ancAMRCSummary$'F value'[2], digits = 2)`, *p* = `r format.pval(ancAMRCSummary$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, 
or for non-attuned mind-related comments, *F*(`r round(ancNMRC$rank-1, digits = 0)`, `r round(ancNMRC$df.residual, digits = 0)`) = `r round(ancNMRCSummary$'F value'[2], digits = 2)`, *p* = `r format.pval(ancNMRCSummary$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`.

Table 2 also shows the data for the separate categories of mind-related comments. Cultural differences in the separate categories of appropriate mind-related comments were investigated using MANCOVA, with the separate categories added as dependent variables, nationality added as a fixed variable, and infant age, maternal education, HADS scores, the PSI-SF subscale scores (parenting distress, parent–child dysfunctional interaction, difficult child), and Lab-TAB scores added as covariates. 
There was a main effect of nationality, *F*(`r round(as.numeric(mancAMRCSummary[[4]][5]), digits = 0)`, `r round(as.numeric(mancAMRCSummary[[4]][6]), digits = 0)`) = `r round(as.numeric(mancAMRCSummary[[4]][4]), digits = 2)`, *p* = `r format.pval(as.numeric(mancAMRCSummary[[4]][7]), digits = 1, eps = 0.001, nsmall = 3)`. 
Follow-up tests showed a main effect of nationality on appropriate comments on (a) desires and preferences, *F*(`r round(phADap$Df[2], digits = 0)`, `r round(phADap$Df[10], digits = 0)`) = `r round(phADap$'F value'[2], digits = 2)`, *p* = `r format.pval(phADap$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`,
(b) cognition, *F*(`r round(phACog$Df[2], digits = 0)`, `r round(phACog$Df[10], digits = 0)`) = `r round(phACog$'F value'[2], digits = 2)`, *p* = `r format.pval(phACog$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`,
and (c) emotion, *F*(`r round(phAEmo$Df[2], digits = 0)`, `r round(phAEmo$Df[10], digits = 0)`) = `r round(phAEmo$'F value'[2], digits = 2)`, *p* = `r format.pval(phAEmo$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`;
there was no main effect of nationality on intention, *F*(`r round(phAInt$Df[10], digits = 0)`, `r round(phAInt$Df[9], digits = 0)`) = `r round(phAInt$'F value'[2], digits = 2)`, *p* = `r format.pval(phAInt$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`.
British mothers commented more frequently in appropriate ways on their infants’ desires and preferences than did Korean mothers, but Korean mothers made more appropriate mind-related comments about their infants’ cognitive and emotional states compared with British mothers (see Table 2).

Cultural differences in the separate categories of non-attuned mind-related comments were investigated using MANCOVA as described above. 
There was a main effect of nationality, *F*(`r round(as.numeric(mancNMRCSummary[[4]][5]), digits = 0)`, `r round(as.numeric(mancNMRCSummary[[4]][6]), digits = 0)`) = `r round(as.numeric(mancNMRCSummary[[4]][4]), digits = 2)`, *p* = `r format.pval(as.numeric(mancNMRCSummary[[4]][7]), digits = 1, eps = 0.001, nsmall = 3)`. 
Follow-up tests showed a main effect of nationality on non-attuned comments on (a) 
desires and preferences, *F*(`r round(phNDap$Df[2], digits = 0)`, `r round(phNDap$Df[10], digits = 0)`) = `r round(phNDap$'F value'[2], digits = 2)`, *p* = `r format.pval(phNDap$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, (b) 
emotion, *F*(`r round(phNEmo$Df[2], digits = 0)`, `r round(phNEmo$Df[10], digits = 0)`) = `r round(phNEmo$'F value'[2], digits = 2)`, *p* = `r format.pval(phNEmo$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, and (c)
physical states, *F*(`r round(phNPhy$Df[2], digits = 0)`, `r round(phNPhy$Df[10], digits = 0)`) = `r round(phNPhy$'F value'[2], digits = 2)`, *p* = `r format.pval(phNPhy$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`;
there was no main effect of nationality on cognition, *F*(`r round(phNCog$Df[2], digits = 0)`, `r round(phNCog$Df[10], digits = 0)`) = `r round(phNCog$'F value'[2], digits = 2)`, *p* = `r format.pval(phNCog$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, 
or intention, *F*(`r round(phNInt$Df[10], digits = 0)`, `r round(phNInt$Df[9], digits = 0)`) = `r round(phNInt$'F value'[2], digits = 2)`, *p* = `r format.pval(phNInt$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`. 
British mothers commented more frequently in non-attuned ways on their infants’ desires and preferences than did Korean mothers, but Korean mothers made more non-attuned mind-related comments about their infants’ emotional and physical states compared with British mothers (see Table 2).

The PRF data are shown in Table 2 as a function of nationality. Cultural differences in PRF were investigated using MANCOVA, with scores for *Certainty about mental states* and *Interest and curiosity about mental states* added as dependent variables, nationality added as a fixed variable, and infant age, maternal education, HADS scores, the PSI-SF subscale scores (parenting distress, parent–child dysfunctional interaction, difficult child), and Lab-TAB scores added as covariates. The correlations between the variables are shown in supplemental material 1. There was a main effect of nationality, *F*(`r round(as.numeric(mancPRFSummary[[4]][5]), digits = 0)`, `r round(as.numeric(mancPRFSummary[[4]][6]), digits = 0)`) = `r round(as.numeric(mancPRFSummary[[4]][4]), digits = 2)`, *p* = `r format.pval(as.numeric(mancPRFSummary[[4]][7]), digits = 1, eps = 0.001, nsmall = 3)`. 
Follow-up tests showed a main effect of nationality on *Certainty about mental states*, 
*F*(`r round(phPCms$Df[2], digits = 0)`, `r round(phPCms$Df[10], digits = 0)`) = `r round(phPCms$'F value'[2], digits = 2)`, *p* = `r format.pval(phPCms$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, but not *Interest and curiosity in mental states*, 
*F*(`r round(phPIac$Df[2], digits = 0)`, `r round(phPIac$Df[10], digits = 0)`) = `r round(phPIac$'F value'[2], digits = 2)`, *p* = `r format.pval(phPIac$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`. As shown in Table 2, 
Korean mothers scored more highly than British mothers for *Certainty about mental states*.

@@

Finally, relations between the two constructs of parental mentalization were explored. Correlations between appropriate and non-attuned mind-related comments and the PRF subscales were run separately for the British and Korean mothers. As shown in Table 3, there were no relations between the mind-mindedness and PRF variables in either British or Korean mothers, with negligible to small effects for all correlations. Given that effect sizes in this range were predicted, additional Bayesian analyses were conducted to verify the null findings (see Table 3). We set the Bayes factor to BF01 to indicate the strength of evidence in favor of the null hypothesis. For the UK sample, the Bayesian analyses indicate strong support for the null hypothesis for the correlation between appropriate mind-related comments and *Certainty about mental states*, and moderate support for the null hypothesis for the correlation between (a) appropriate comments and *Interest and curiosity in mental states*, (b) non-attuned comments and *Certainty about mental states*, and (c) non-attuned comments and *Interest and curiosity in mental states*. For the Korean sample, the Bayesian analyses indicate moderate support for the null hypothesis for the correlation between (a) appropriate mind-related comments and *Certainty about mental states*, (b) appropriate comments and *Interest and curiosity in mental states*, and (c) non-attuned comments and *Certainty about mental states*, and anecdotal support for the null hypothesis for the correlation between non-attuned comments and *Interest and curiosity in mental states*. Note that the correlations between *Interest and curiosity in mental states* and non-attuned mind-related comments are positive in the Korean sample.

@@

<div id="refs"></div>

# Supplementary Materials {.unnumbered}

  #create number & text combos to be inputted into cells (e.g. mean(SD)).
  GBMSD <- paste0(round (tTest$estimate[2], digits = 2), " (", (round (sd(GB[[val]], na.rm=TRUE), digits = 2)), ")")
  KOMSD <- paste0(round (tTest$estimate[1], digits = 2), " (", (round (sd(KO[[val]], na.rm=TRUE), digits = 2)), ")")
  tTestSum <- paste0("t(",  (round(tTest$parameter['df'], digits = 0)),  ") = ", (round(tTest$statistic['t'], digits = 2)))

```{r Table3prep, echo=FALSE}

>>>>

Two British mothers did not answer the age question, and another British mother’s HADS and PSI-SF responses could not be used due to a technical problem. The mother with missing HADS and PSI-SF data was excluded from the main analyses on cultural differences in parental mentalization reported below. 
Korean infants were older than British infants, *t*(`r round(iAge$parameter['df'], digits = 0)`) = `r round(iAge$statistic['t'], digits = 2)`, *p* = `r format.pval(iAge$p.value, digits = 1, eps = 0.001, nsmall = 3)`,
and British mothers were more highly educated than Korean mothers, *t*(`r round(mEdu$parameter['df'], digits = 0)`) = `r round(mEdu$statistic['t'], digits = 2)`, *p* = `r format.pval(mEdu$p.value, digits = 1, eps = 0.001, nsmall = 3)`, 
but the groups did not differ on maternal age, *t*(`r round(mAge$parameter['df'], digits = 0)`) = `r round(mAge$statistic['t'], digits = 2)`, *p* = `r format.pval(mAge$p.value, digits = 1, eps = 0.001, nsmall = 3)`. 
Infant age and maternal education were therefore included as additional covariates in the cultural differences analyses reported below. With regard to the separate categories of mind-related comments, only two mothers mentioned epistemic states and only eight mothers talked on the infant’s behalf. These categories are therefore not used in the analyses below. Table \@ref(tab:table1) shows the parenting style, mental health, and infant temperament data as a function of nationality. As shown Table \@ref(tab:table1), British mothers showed more positive parenting than did their Korean counterparts for both the self-report and observational measures. In terms of psychological well-being, Korean mothers scored more highly than British mothers for anxiety/depression and parenting distress. However, there were no significant differences between British and Korean mothers for reported or observed infant temperament and parent–child dysfunctional interaction (see Table \@ref(tab:table1)).

  #create number & text combos to be inputted into cells (e.g. mean(SD)).
  GBMSD <- paste0(round (tTest$estimate[2], digits = 2), " (", (round (sd(GB[[val]], na.rm=TRUE), digits = 2)), ")")
  KOMSD <- paste0(round (tTest$estimate[1], digits = 2), " (", (round (sd(KO[[val]], na.rm=TRUE), digits = 2)), ")")
  tTestSum <- paste0("t(",  (round(tTest$parameter['df'], digits = 0)),  ") = ", (round(abs(tTest$statistic['t']), digits = 2)))

@@

Table \@ref(tab:table2) shows the mind-mindedness data for the UK and Korean samples. Cultural differences in appropriate and non-attuned mind-related comments were investigated using ANCOVA, with nationality added as a fixed variable and infant age, maternal education, HADS scores, the PSI-SF subscale scores (parenting distress, parent–child dysfunctional interaction, difficult child), and Lab-TAB scores added as covariates. The correlations between the variables are shown in supplemental material 1. 
There was no main effect of nationality for appropriate mind-related comments, *F*(`r round(ancAMRC$rank-1, digits = 0)`, `r round(ancAMRC$df.residual, digits = 0)`) = `r round(ancAMRCSummary$'F value'[2], digits = 2)`, *p* = `r format.pval(ancAMRCSummary$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, 
or for non-attuned mind-related comments, *F*(`r round(ancNMRC$rank-1, digits = 0)`, `r round(ancNMRC$df.residual, digits = 0)`) = `r round(ancNMRCSummary$'F value'[2], digits = 2)`, *p* = `r format.pval(ancNMRCSummary$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`.

Table \@ref(tab:table2) also shows the data for the separate categories of mind-related comments. Cultural differences in the separate categories of appropriate mind-related comments were investigated using MANCOVA, with the separate categories added as dependent variables, nationality added as a fixed variable, and infant age, maternal education, HADS scores, the PSI-SF subscale scores (parenting distress, parent–child dysfunctional interaction, difficult child), and Lab-TAB scores added as covariates. 
There was a main effect of nationality, *F*(`r round(as.numeric(mancAMRCSummary[[4]][5]), digits = 0)`, `r round(as.numeric(mancAMRCSummary[[4]][6]), digits = 0)`) = `r round(as.numeric(mancAMRCSummary[[4]][4]), digits = 2)`, *p* = `r format.pval(as.numeric(mancAMRCSummary[[4]][7]), digits = 1, eps = 0.001, nsmall = 3)`. 
Follow-up tests showed a main effect of nationality on appropriate comments on (a) desires and preferences, *F*(`r round(phADap$Df[2], digits = 0)`, `r round(phADap$Df[10], digits = 0)`) = `r round(phADap$'F value'[2], digits = 2)`, *p* = `r format.pval(phADap$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`,
(b) cognition, *F*(`r round(phACog$Df[2], digits = 0)`, `r round(phACog$Df[10], digits = 0)`) = `r round(phACog$'F value'[2], digits = 2)`, *p* = `r format.pval(phACog$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`,
and (c) emotion, *F*(`r round(phAEmo$Df[2], digits = 0)`, `r round(phAEmo$Df[10], digits = 0)`) = `r round(phAEmo$'F value'[2], digits = 2)`, *p* = `r format.pval(phAEmo$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`;
there was no main effect of nationality on intention, *F*(`r round(phAInt$Df[10], digits = 0)`, `r round(phAInt$Df[9], digits = 0)`) = `r round(phAInt$'F value'[2], digits = 2)`, *p* = `r format.pval(phAInt$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`.
British mothers commented more frequently in appropriate ways on their infants’ desires and preferences than did Korean mothers, but Korean mothers made more appropriate mind-related comments about their infants’ cognitive and emotional states compared with British mothers (see Table \@ref(tab:table2)).

Cultural differences in the separate categories of non-attuned mind-related comments were investigated using MANCOVA as described above. 
There was a main effect of nationality, *F*(`r round(as.numeric(mancNMRCSummary[[4]][5]), digits = 0)`, `r round(as.numeric(mancNMRCSummary[[4]][6]), digits = 0)`) = `r round(as.numeric(mancNMRCSummary[[4]][4]), digits = 2)`, *p* = `r format.pval(as.numeric(mancNMRCSummary[[4]][7]), digits = 1, eps = 0.001, nsmall = 3)`. 
Follow-up tests showed a main effect of nationality on non-attuned comments on (a) 
desires and preferences, *F*(`r round(phNDap$Df[2], digits = 0)`, `r round(phNDap$Df[10], digits = 0)`) = `r round(phNDap$'F value'[2], digits = 2)`, *p* = `r format.pval(phNDap$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, (b) 
emotion, *F*(`r round(phNEmo$Df[2], digits = 0)`, `r round(phNEmo$Df[10], digits = 0)`) = `r round(phNEmo$'F value'[2], digits = 2)`, *p* = `r format.pval(phNEmo$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, and (c)
physical states, *F*(`r round(phNPhy$Df[2], digits = 0)`, `r round(phNPhy$Df[10], digits = 0)`) = `r round(phNPhy$'F value'[2], digits = 2)`, *p* = `r format.pval(phNPhy$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`;
there was no main effect of nationality on cognition, *F*(`r round(phNCog$Df[2], digits = 0)`, `r round(phNCog$Df[10], digits = 0)`) = `r round(phNCog$'F value'[2], digits = 2)`, *p* = `r format.pval(phNCog$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, 
or intention, *F*(`r round(phNInt$Df[9], digits = 0)`, `r round(phNInt$Df[10], digits = 0)`) = `r round(phNInt$'F value'[2], digits = 2)`, *p* = `r format.pval(phNInt$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`. 
British mothers commented more frequently in non-attuned ways on their infants’ desires and preferences than did Korean mothers, but Korean mothers made more non-attuned mind-related comments about their infants’ emotional and physical states compared with British mothers (see Table \@ref(tab:table2)).

The PRF data are shown in Table \@ref(tab:table2) as a function of nationality. Cultural differences in PRF were investigated using MANCOVA, with scores for *Certainty about mental states* and *Interest and curiosity about mental states* added as dependent variables, nationality added as a fixed variable, and infant age, maternal education, HADS scores, the PSI-SF subscale scores (parenting distress, parent–child dysfunctional interaction, difficult child), and Lab-TAB scores added as covariates. The correlations between the variables are shown in supplemental material 1. There was a main effect of nationality, *F*(`r round(as.numeric(mancPRFSummary[[4]][5]), digits = 0)`, `r round(as.numeric(mancPRFSummary[[4]][6]), digits = 0)`) = `r round(as.numeric(mancPRFSummary[[4]][4]), digits = 2)`, *p* = `r format.pval(as.numeric(mancPRFSummary[[4]][7]), digits = 1, eps = 0.001, nsmall = 3)`. 
Follow-up tests showed a main effect of nationality on *Certainty about mental states*, 
*F*(`r round(phPCms$Df[2], digits = 0)`, `r round(phPCms$Df[10], digits = 0)`) = `r round(phPCms$'F value'[2], digits = 2)`, *p* = `r format.pval(phPCms$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`, but not *Interest and curiosity in mental states*, 
*F*(`r round(phPIac$Df[2], digits = 0)`, `r round(phPIac$Df[10], digits = 0)`) = `r round(phPIac$'F value'[2], digits = 2)`, *p* = `r format.pval(phPIac$'Pr(>F)'[2], digits = 1, eps = 0.001, nsmall = 3)`. As shown in Table \@ref(tab:table2), 
Korean mothers scored more highly than British mothers for *Certainty about mental states*.

@@

Finally, relations between the two constructs of parental mentalization were explored. Correlations between appropriate and non-attuned mind-related comments and the PRF subscales were run separately for the British and Korean mothers. As shown in Table \@ref(tab:table3), there were no relations between the mind-mindedness and PRF variables in either British or Korean mothers, with negligible to small effects for all correlations. Given that effect sizes in this range were predicted, additional Bayesian analyses were conducted to verify the null findings (see Table \@ref(tab:table3)). We set the Bayes factor to BF01 to indicate the strength of evidence in favor of the null hypothesis. For the UK sample, the Bayesian analyses indicate strong support for the null hypothesis for the correlation between appropriate mind-related comments and *Certainty about mental states*, and moderate support for the null hypothesis for the correlation between (a) appropriate comments and *Interest and curiosity in mental states*, (b) non-attuned comments and *Certainty about mental states*, and (c) non-attuned comments and *Interest and curiosity in mental states*. For the Korean sample, the Bayesian analyses indicate moderate support for the null hypothesis for the correlation between (a) appropriate mind-related comments and *Certainty about mental states*, (b) appropriate comments and *Interest and curiosity in mental states*, and (c) non-attuned comments and *Certainty about mental states*, and anecdotal support for the null hypothesis for the correlation between non-attuned comments and *Interest and curiosity in mental states*. Note that the correlations between *Interest and curiosity in mental states* and non-attuned mind-related comments are positive in the Korean sample.

```{r table3, echo=FALSE}

@@
